\documentclass{article}
\title{Student Organization Constitution}
\date{}

\begin{document}
\maketitle

\begin{enumerate}

\item
  The name of this organization shall be: Artificial Intelligence Group

\item
  The purpose of this organzation shall be to: 
  \begin{itemize}
    \item Develop the skills and knowledge of the membership regarding Artificial Intelligence. 
    \item Apply Artificial Intelligence research to solve challenging problems.
  \end{itemize}

\item The Aurthorized Representatives, officers, and members of this organization:
  \begin{itemize}
    \item 
      Accept responsibility for compliance with University policies and campus regulations.
    \item 
      Understand and agree to abide by the provisions of the anti-hazing statues in the California Education Code or Penal Code (as ammended, effective January $1^{st}$, 2007).
    \item
      Affirm that the rules, regulations and policies of the University of California and UCSC shall supersede the rules, regulations, policies and/or bylaws of any affiliated international national, regional or local organization.
      
  \end{itemize}

\item
  In addition, the membership criteria of this organization shall be:
  \begin{itemize}
    \item 
      All UCSC students interested in the purpose of this organization are eligible for membership.
    \item
      Membership is open to any student regardless of gender, ethnicity,religion, etc. with the exception of incorporated sororities and fraternities, which may be limited by gender.
    \item
      Membership is limited to currently registered UCSC students. Non-students are welcome to participate in activities, but may not be members, hold office, or vote. Non-students must complete non-student participation forms.
    \item
      Any UCSC Alumni who had membership in the Artificial Intelligence Group and any UCSC staff member is elligible to be an Organization Advisor if approved by an officer. 
  \end{itemize}

\item
  Membership may be recinded by either Officer Measure or Public Measure.

\item
  Qualifications for Officers/Authroized Representatives:
  \begin{itemize}
    \item
      Officers and Authorized Representatives are assigned by agreement of both Organization Presidents. 
    \item
      Must have sufficient knowledge of and experience with Artificial Intelligence. 
  \end{itemize}

\item
  Duties and responsibilites of Officers/Authroized Representatives
  \begin{itemize}

    \item
      President
      \begin{itemize}
      \item There must be at all times two Presidents. 
      \item The Presidents assign organization Officers/Authorized Representatives.
      \item The Presidents must be available to make Presidential decisions in a timely manner. 
      \end{itemize}
    \item All Officers
      \begin{itemize}
        \item Officers determine dates and times for officer meetings and public meetings.
        \item Officers are required to attend all designated officer meetings. 
        \item Officers are required to participate in all Officer Measures. 
      \end{itemize}
    \item
      Vice-President
      \begin{itemize}
      \item The Vice-President is responsible for responding to any public request for an Officer Measure.
      \item The Vice-President is responsible for communicating Officer Measure decisions to the membership. 
      \item The Vice-President manages any conflict within the membership
      \end{itemize}
      
    \item
      Fiscal Representative
      \begin{itemize}
        \item The Fiscal Representative is responsible for managing the UCSC organization account, all expenditures, and any funds raised. 
      \end{itemize}
    \item
      Other Officer Positions
      \begin{itemize}
        \item Other positions may be created by unanimous Presidential decision, the responsibilities and dutes of which will be recorded and available to the membership.  
      \end{itemize}

  \end{itemize}

\item
  Election and removal of Officers/Authorized Representatives
  \begin{itemize}
    \item
      Officers/Authorized Representatives are assigned by the Presidents. 
    \item
      Presidents are elected by Public Measure at the end of each Spring quarter. The president serves for a term of one year and may serve as many consecutive terms as the membership wishes.
    \item
      Officers/Authorized Representatives can be removed by Officer Measure or by unanimous Presidential decision. 
    \item
      A President may be removed by agreement of the Officers, the Membership, and the other President. The Officer Measure must pass with $3/4$ support, a Public Measure must pass, and the other President must agree.
  \end{itemize}

\item
  Organization decision-making:
  \begin{enumerate}
  \item
    The organization shall make two categories of decisions: 
    \begin{enumerate}
    \item
      Officer Measures: 
      \begin{enumerate}
        \item Any decision regarding the spending of the organization's funds
        \item Any change to the constitution.
      \end{enumerate}
    \item
      Public Measure: A Public Measure can decide on anything not explicity designated as requiring an officer measure.
    \end{enumerate}

  \item
    Quorum shall be: 
    \begin{enumerate}
      \item Officer Measures: A quorum of officers for an Officer Measure is a majority of officers excluding presidents, as well as both presidents in agreement.
      \item Public Measures: There is no quorum of membership for a public decision. These decisions are decided via Instant Runoff Voting. 
    \end{enumerate}

  \item
    Voting shall be granted to all members for public decisions.
  \item
    Public decisions shall be made using the Instant Runoff Voting format. A request for a vote on a Public Measure can be made by $30\%$ of the membership body. 
  \item
    A request by the membership for a vote on an Officer Measure can be made by $30\%$ of the membership body.
    
  \end{enumerate}

\item
  Financial records procedure: The Financial Officer is charged with ensuring that all earnings and spendings are recorded at their discretion. Any spending of organization funds must be approved as an Officer Measure.

\item
  Ammendments to the Constituion shall be made by Officer Measure, which may be prompted by the membership. 

\end{enumerate}

\begin{tabular}{l}
  \makebox[3in]{\hrulefill}\\
  Name of Authorized Representative
\end{tabular}
\\
\\

\begin{tabular}{ll}
  \makebox[3in]{\hrulefill} & \makebox[2in]{\hrulefill}\\
  Signature & Date
\end{tabular}

\end{document}
