\documentclass{article}
\title{Homework 1}
\author{John Carlyle}

\usepackage[margin=1in]{geometry}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}

\newcommand{\BigO}[1]{\ensuremath{\operatorname{O}\bigl(#1\bigr)}}

\begin{document}
\maketitle

\begin{enumerate}
\item \hfill
  \paragraph{Symmetric cipher}{A symmetric cipher (single-key encryption) is a cipher such that given a plaintext $P$, a key $K$, an encryption algorithm $E$, and a decryption algorithm $D$ the following is true: $P = D(E(P,K),K)$. In other words after encrypting with $K$ the way you get the message back is to call $D$ with the same key $K$.}
  \paragraph{}{Since the key has to be the same it is a requirement that both parties involved have access to the key. Both parties must have at some point agreed upon a key to use. Since the key is used to decrypt as well as encrypt this means that in most cases the decryption algorithm is bascially the encription algorithm in reverse. A final requirement given by the book is that the encryption algorithm has to be strong enough to withstand an opponent who has access to multiple ciphertexts that use the same key. I assume this is because the key sharing problem may mean that the same key is reused often between parties using this method to communicate. If they could exchange a key safely, why can't they just exchange the message itself through this safe channel?}
\item \hfill
  \paragraph{Linear function block cipher}{A choice of each bit in the 128 bits as a 1 while the rest are 0s would allow one to combine via xor to make any bit pattern. And since we know each of the individual ciphertexts plaintext equivilent we can split it since EL is a linear operator and decrypt each piece individually. We get to know the plaintext since we choose those 128 plaintexts specifically. Now they get xored together to show us the original message. Very insecure!}
\item \hfill 
  \paragraph{Substitution cipher}{My first idea was to re-write a program I had written to break the simple substitution cipher on the cards against humanity 12 days of christmas puzzle. A program that just looked at letter frequency and a dictionary. But what fun would that be? Instead I decided to see if a genetic algorithm could crack it. Instead of just launcing into it I first looked for some research on the topic online and found this: \url{http://people.cs.uct.ac.za/~jkenwood/JasonBrownbridge.pdf} I stole all his constants and techniques for selection, touranments, elitism, mutation, population and crossover. Since all the aformentioned constants are hard guess well on the first try and can take awhile to tune, which isn't much fun.}
  \paragraph{Implementation}{I implemented the GA in python (see attached file ga-1.py), and used trigram frequencies to calculate the fitness of each key. The common english trigrams were initially collected by scanning A Tale of Two Cities by Charles Dickens. After the first attempt at decrypting the cyphertext (100 generations) I had recieved the following result as my fittest individual (key):}

  \begin{center}
    KEY: BDFJKHMAWTVPGULNYZCXSIOEQR, Fitness: 11796.3075445
  \end{center}
  \tiny
  \begin{tabular}{llllllllllll}
    SECRE&TNSAE&AVESD&ROPPI&NGISS&TILLI&NTHEN&EWSDE&TAILS&ABOUT&ONCES&ECRET\\
    PROGR&AMSCO&NTINU&ETOLE&AKTHE&DIREC&TOROF&NATIO&NALIN&TELLI&GENCE&HASRE\\
    CENTL&YDECL&ASSIF&IEDAD&DITIO&NALIN&FORMA&TIONA&NDTHE&PRESI&DENTS&REVIE\\
    WGROU&PHASZ&USTRE&LEASE&DITSR&EPORT&ANDRE&COMME&NDATI&ONSWI&THALL&THISG\\
    OINGO&NITSE&ASYTO&BECOM&EINUR&EDTOT&HEBRE&ADTHA&NDDEP&THOFT&HENSA&SACTI\\
    VITIE&SBUTT&HROUG&HTHED&ISCLO&SURES&WEVEL&EARNE&DANEN&ORMOU&SAMOU&NTABO\\
    UTTHE&AGENC&YSCAP&ABILI&TIESH&OWITI&SFAIL&INGTO&PROTE&CTUSA&NDWHA&TWENE\\
    EDTOD&OTORE&GAINS&ECURI&TYINT&HEINF&ORMAT&IONAG&EFIRS&TANDF&OREMO&STTHE\\
    SURVE&ILLAN&CESTA&TEISR&OBUST&ITISR&OBUST&POLIT&ICALL&YLEGA&LLYAN&DTECH\\
    NICAL&LYICA&NNAME&THREE&DIFFE&RENTN&SAPRO&GRAMS&TOCOL&LECTG&MAILU&SERDA\\
    TATHE&SEPRO&GRAMS&AREBA&SEDON&THREE&DIFFE&RENTT&ECHNI&CALEA&VESDR&OPPIN\\
    GCAPA&BILIT&IESTH&EYREL&YONTH&REEDI&FFERE&NTLEG&ALAUT&HORIT&IESTH&EYINV\\
    OLVEC&OLLAB&ORATI&ONSWI&THTHR&EEDIF&FEREN&TCOMP&ANIES&ANDTH&ISISZ&USTGM\\
    AILTH&ESAME&ISTRU&EFORC&ELLPH&ONECA&LLREC&ORDSI&NTERN&ETCHA&TSCEL&LPHON\\
    ELOCA&TIOND&ATASE&CONDT&HENSA&CONTI&NUEST&OLIEA&BOUTI&TSCAP&ABILI&TIESI\\
    THIDE&SBEHI&NDTOR&TURED&INTER&PRETA&TIONS&OFWOR&DSLIK&ECOLL&ECTIN&CIDEN\\
    TALLY&TARGE&TANDD&IRECT&EDITC&LOAKS&PROGR&AMSIN&MULTI&PLECO&DENAM&ESTOO\\
    BSCUR&ETHEI&RFULL&EXTEN&TANDC&APABI&LITIE&SOFFI&CIALS&TESTI&FYTHA&TAPAR\\
    TICUL&ARSUR&VEILL&ANCEA&CTIVI&TYISN&OTDON&EUNDE&RONEP&ARTIC&ULARP&ROGRA\\
    MORAU&THORI&TYCON&VENIE&NTLYO&MITTI&NGTHA&TITIS&DONEU&NDERS&OMEOT&HERPR\\
    OGRAM&ORAUT&HORIT&YTHIR&DUSGO&VERNM&ENTSU&RVEIL&LANCE&ISNOT&ZUSTA&BOUTT\\
    HENSA&THESN&OWDEN&DOCUM&ENTSH&AVEGI&VENUS&EXTRA&ORDIN&ARYDE&TAILS&ABOUT\\
    THENS&ASACT&IVITI&ESBUT&WENOW&KNOWT&HATTH&ECIAN&ROFBI&DEAAN&DLOCA&LPOLI\\
    CEALL&ENGAG&EINUB&IQUIT&OUSSU&RVEIL&LANCE&USING&THESA&MESOR&TSOFE&AVESD\\
    ROPPI&NGTOO&LSAND&THATT&HEYRE&GULAR&LYSHA&REINF&ORMAT&IONWI&THEAC&HOTHE\\
    R
  \end{tabular}
  \normalsize

  \paragraph{First result}{This key seemed to have one or two inversions left in it but the text was clearly about the NSA and security. So I choose a different training text, The Shadow Factory by James Bamford. After training on a text with similar words in it the average fitness of the population rose much more quickly and after convergence gave me the correct key. Below is the key and the messsage with manually added spaces.}

  \paragraph{Key}{BDFZKHMAWTVPGULNYJCXSIOEQR, Fitness: 12796.4907841}
    
  \paragraph{Message:}{SECRET NSA EAVESDROPPING IS STILL IN THE NEWS DETAILS ABOUT ONCE SECRET PROGRAMS 
    CONTINUE TO LEAK THE DIRECTOR OF NATIONAL INTELLIGENCE HAS RECENTLY DECLASSIFIED 
    ADDITIONAL INFORMATION AND THE PRESIDENTS REVIEW GROUP HAS JUST RELEASED ITS
    REPORT AND RECOMMENDATIONS WITH ALL THIS GOING ON ITS EASY TO BECOME INURED TO 
    THE BREADTH AND DEPTH OF THE NSAS ACTIVITIES BUT THROUGH THE DISCLOSURES WEVE 
    LEARNED AN ENORMOUS AMOUNT ABOUT THE AGENCYS CAPABILITIES HOW IT IS FAILING TO 
    PROTECT US AND WHAT WE NEED TO DO TO REGAIN SECURITY IN THE INFORMATION AGE FIRST 
    AND FOREMOST THE SURVEILLANCE STATE IS ROBUST IT IS ROBUST POLITICALLY LEGALLY AND TECHNICALLY 
    I CAN NAME THREE DIFFERENT NSA PROGRAMS TO COLLECT GMAIL USER DATA THESE PROGRAMS 
    ARE BASED ON THREE DIFFERENT TECHNICAL EAVESDROPPING CAPABILITIES THEY RELY ON 
    THREE DIFFERENT LEGAL AUTHORITIES THEY INVOLVE COLLABORATIONS WITH THREE DIFFERENT 
    COMPANIES AND THIS IS JUST GMAIL THE SAME IS TRUE FOR CELLPHONE CALL RECORDS 
    INTERNET CHATS CELLPHONE LOCATION DATA SECOND THE NSA CONTINUES TO LIE ABOUT ITS 
    CAPABILITIES IT HIDES BEHIND TORTURED INTERPRETATIONS OF WORDS LIKE COLLECT 
    INCIDENTALLY TARGET AND DIRECTED IT CLOAKS PROGRAMS IN MULTIPLE CODE NAMES TO 
    OBSCURE THEIR FULL EXTENT AND CAPABILITIES OFFICIALS TESTIFY THAT A PARTICULAR SURVEILLANCE 
    ACTIVITY IS NOT DONE UNDER ONE PARTICULAR PROGRAM OR AUTHORITY CONVENIENTLY OMITTING 
    THAT IT IS DONE UNDER SOME OTHER PROGRAM OR AUTHORITY THIRD US GOVERNMENT SURVEILLANCE 
    IS NOT JUST ABOUT THE NSA THE SNOWDEN DOCUMENTS HAVE GIVEN US EXTRAORDINARY DETAILS 
    ABOUT THE NSAS ACTIVITIES BUT WE NOW KNOW THAT THE CIA NRO FBI DEA AND LOCAL POLICE ALL 
    ENGAGE IN UBIQUITOUS SURVEILLANCE USING THE SAME SORTS OF EAVESDROPPING TOOLS AND THAT
    THEY REGULARLY SHARE INFORMATION WITH EACHOTHER}


\item \hfill 
  \paragraph{Vigenere Cipher}{The first step to solving the vigenier cipher is to find the size of the key using index of coincidence. My program (attached as solv-2.py) when passed the k option and two keysizes seperated by a colon will try seperating the text into a matrix based on that key size and calculate the IC of each column. Each column is assumed to be the letters translated by the same letter of the key if the key length is equal to the width of the matrix. The results are sorted by the IC and returned to the user to show the most probable key length first. The result of running this program is shown below.}

  \begin{center}
    \begin{tabular}{l}
      \$ python solv-2.py -k 3:29 hw1-2.crypt\\
      (12, 1.707807386629266)\\
      (20, 1.5194805194805194)\\
      (10, 1.3886743886743886)\\
      (24, 1.3228492136910268)\\
      (6, 1.2981110142400465)\\
      (21, 1.2264150943396226)\\
      (3, 1.2167552997741677)\\
      (4, 1.2087369815339064)\\
      (23, 1.193877551020408)\\
      (17, 1.187878787878788)\\
      (8, 1.133145657387134)\\
      .\\
      .\\
      .\\
    \end{tabular}
  \end{center}

  \paragraph{Key length}{These results hint that the keylength is most likely 12, 20 or 10 since they have the highest index of coincidence. ga-2.py was used to test a keylength of 12 and see if it could find any keys that yielded english looking text using the exact same technique from the first decryption problem. Again the GA was trained on The Shadow Factory because I assumed that the text had similar content to the first one.}

  \begin{center}
    \begin{tabular}{l}
      \$ python ga-2.py -l 12 hw1-2.crypt\\
      Geneation 1 best individual: (YTLHJKJOEUUH) 3048.749782 \\
      Geneation 2 best individual: (AFZVIFBEWJUF) 3927.156567 \\
      Geneation 3 best individual: (ARZVIFJFKUUH) 4671.765319 \\
      Geneation 4 best individual: (AFZVIFBEKUUH) 6447.459217 \\
      Geneation 5 best individual: (RXFFIFBEKUUH) 6554.993247 \\
      Geneation 6 best individual: (AXFVIFBEKUUH) 7835.351044 \\
      Geneation 7 best individual: (AFFGVFBEKUUH) 8194.710882 \\
      Geneation 8 best individual: (AXFGVFBEKUUH) 9500.430740 \\
      Geneation 9 best individual: (AXFGVFBEKUUH) 9500.430740\\
    \end{tabular}
  \end{center}
  
  \paragraph{Solution}{The GA converged after 8 generations giving us the key YTLHJKJOEUUH. It looks like the GA got a little lucky successfully guessing the last three letters in the first generation. After pulling the data out of the gen8 file I fixed the spacing to by hand. The final result is shown below:}

  \begin{paragraph}{Message:}
    PRESIDENT BARACK OBAMA IS EXPECTED TO ANNOUNCE CHANGES ON FRIDAY TO SWEEPING
    US SURVEILLANCE EFFORTS EXPOSED BY INTELLIGENCE LEAKER EDWARD SNOWDEN WHOSE BLOCKBUSTER
    DISCLOSURES HAVE RAISED QUESTIONS ABOUT GOVERNMENT OVERREACH IN FIGHTING TERROR
    THE SCOPE OF PHONE AND EMAIL SNOOPING BY THE NATIONAL SECURITY AGENCY THAT CAME TO
    LIGHT LAST YEAR TRIGGERED OUTRAGE FROM CIVIL LIBERTARIANS AND PROMPTED KEY MEMBERS 
    OF CONGRESS FROM BOTH PARTIES TO WEIGH CHANGES IN NATIONAL SECURITY LAW OBAMA IS 
    EXPECTED TO ACT ON RECOMMENDATIONS FROM AN INDEPENDENT PANEL THAT HE CALLED FOR 
    AT THE HEIGHT OF THE FALLOUT FROM THE LEAKS AROUND THE AGENCYS SURVEILLANCE 
    ACTIVITIES AND A SECRET COURT THAT WORKS WITH IT THE PRESIDENT IAL REVIEW GROUP 
    ON INTELLIGE NCE CONCLUDED IN DECEMBER THAT DATA COLLECTION SHOULD REMAIN BUT 
    THAT THE GOVERNMENT MUST DO A BETTER JOB OF PROTECTING CIVIL LIBERTIES IN THE 
    CONTEXT OF NATIONAL SECURITY CHANGES IMPOSED BY THE PRESIDENT WILL PERMANENTLY 
    PLACE HIS SIGNATURE ON THE INTELLIGENCE INITIATIVE AND HELP DEFINE HIS LEGACY
    AS A CHIEF EXECUTIVE WHO PROMISED A MORE OPEN AND TRANSPARENT GOVERNMENT WHEN HE 
    ENTERED THE WHITE HOUSE FIVE YEARS AGO NSA DOMESTIC AND INTERNATIONAL PHONE 
    AND EMAIL SURVEILLANCE IS CONS IDEREDSOME OF THE MOST WIDESPREAD INTELLIGENCE 
    GATHERING PERFORMED BY THE US GOVERNMENT
  \end{paragraph}
  
\item \hfill
  \paragraph{Bible 1}{The bible has $\thicksim31000$ verses. So we have that many starting places, and we know the length of the cipher text. It should be a trivial matter to extract the text starting at each verse and keep reading as long as there is more ciphertext. I think it would be \BigO{n} where $n$ is the length of the ciphertext. Not too difficult.}
  
  \paragraph{Bible 2}{Given that we do not know the function to choose the next verse (whereas in the last one we did, it was simply the next verse) it should be a lot harder to figure out the key. Assuming of course that the ciphertext is long enough to span more than one verse we will have to calculate the next verse each time we get to the end of a verse but we still have ciphertext without a key. If we were to brute force it we could simply try all verses, then try all verses as the second verse in the key, then all verses as the third and so on. However this is going to get difficult very fast since we are multiplying by $\thicksim31000$ each time.}

\item \hfill 
  \paragraph{Entropy}{It does not. Entropy is a measure of the information content of the message. As long as a message is recoverable given a ciphertext and a key then the message still contains the content, and therefore it still contains the same entropy.}
\end{enumerate}

\end{document}
