\documentclass[11pt]{article} %Sets the default text size to 11pt and class to article.

\usepackage{changepage}

\pagenumbering{gobble}
\topmargin=0.0in
\oddsidemargin=0.0in
\evensidemargin=0in
\textwidth=6.5in 
\marginparwidth=0.5in
\headheight=0pt
\headsep=0pt
\textheight=9.0in

%%for indented paragraphs
\newenvironment{indentpar}[1]%
 {\begin{list}{}%
         {\setlength{\leftmargin}{#1}}%
         \item[]%
 }
 {\end{list}}

\begin{document}
\centerline {\LARGE \bf John W. Carlyle}
\centerline {831.345.9244 ~~~~~~~~~~ john.w.carlyle@gmail.com}
\bigskip

\noindent {\Large \bf Objective: Instructional Assistant I}
\smallskip
\noindent\\
Focused, creative, efficient, analytical tutor. Technology savvy. Good sense of humor, organized and resourceful in finding elegant solutions. Known as approachable, pragmatic, and possesses a strong work ethic. 
\bigskip

\bigskip
\noindent {\Large \bf Education}\\
\centerline {University of California, Santa Cruz; B.S. in Computer Science, in progress}
\centerline {Cabrillo College; A.A. in Mathematics and A.A. in Computer Science}
\centerline {Skills Certificate: Game programming in Java}
\centerline {Alternative Family Education, graduated 2007}

\bigskip
%%CORE COMPETENCIES
\noindent {\Large \bf Core Competencies}
\smallskip
\begin{center}
  \begin{tabular}{llll}
    Passionate Teacher ~~& Typesetting & Algebra & Linear Algebra\\
    Organized & Programming & Calculus & Differential Equations\\
    Self Motivated & Project Management & Probability & Patient Tutor\\
  \end{tabular}
\end{center}


%%PROFESSIONAL BACKGROUND
\bigskip
\noindent {\Large \bf Professional Background}
\begin{adjustwidth}{0.3in}{0cm}
  \noindent {\large \bf Private Math and Computer Science Tutor \hfill 2005-current}\\
  Designed and implemeted curriculum for Introduction to Computer Science for middle schoolers.
  Assisted graduate students at UCSC in the fields of Bioinformatics, Computational Linguistics, and Programming Languages.

  \bigskip
  \noindent {\large \bf Math Learning Center Tutor\hfill 2010-2012}\\
  Helped students in a variety of math subjects, including review of current material, and aided in test preperation. 
  Transitioned into training new tutors in various teaching methods and best tutoring practices.
  Worked with students at levels ranging from Essential Math, Algebra, Calculus, and Differential Equations. 
  Assisted with troubleshooting and programming of the Polyhedral data tracking program.

  \bigskip
  \noindent {\large \bf Computer Technology Center Tutor\hfill 2010-2012}\\
  Tutored students in every programming language taught at Cabrillo College, as well as Introudction to Algorithms and Datastructures,  and Discrete Math.
\end{adjustwidth}

%%PERSONAL PROJECTS
\bigskip
\noindent {\Large \bf Personal Projects}
\begin{adjustwidth}{.3in}{0cm}
  \noindent {\large \bf Fractal Viewer}\\
  Fractal viewing software using Python and PyGame for rendering many different kinds of fractals. 
  Designed as a teaching instrument to show how a small change in initial parameters can lead to majorly different looking fractals. Repository can be found on github.com/stealthycoin.

  \bigskip
  \noindent {\large \bf Kaleidoscope}\\
  System for generating medium scale websites using low level descriptions of the site requirements in JSON. Deploys website skeleton using Django as the base framework. Currently in the planning stages.
\end{adjustwidth}


\end{document}
